How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-13 docs/PhysicsPaper/StokesErosion.tex
NM

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% TITLE AUTHORS ABSTRACT
\begin{document}
\title{Fluid-mechanical erosion creates anisotropic porous media}

@@

\begin{abstract}
We numerically simulate the erosion of a porous medium due to an internally flowing fluid.  The solid constituents of the porous medium erode under the action of surface shear stress. As the particles disintegrate, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.
\end{abstract}
\maketitle
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% TITLE AUTHORS ABSTRACT
\begin{document}
\title{How fluid-mechanical erosion creates anisotropic porous media}

@@

\begin{abstract}
Using a Cauchy integral formulation of the boundary integral equations, we numerically simulation the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow. The bodies comprising the porous medium are resolved individually and erode under the action of surface shear stress. In particular, microscopic changes in the morphology of the constituents are resolved in detail, and these changes give rise to larger-scale features such as channelization of the medium. The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies.
\end{abstract}
\maketitle

impinging intervening interal

% Original ideas
%We numerically simulate the erosion of a porous medium due to an internally flowing fluid, with solid constituents of the medium eroding under the action of surface shear stress. 
%We numerically simulate the erosion of a porous medium due to an internally flowing fluid.  The solid constituents of the porous medium erode under the action of surface shear stress. As the particles disintegrate, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
